\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english,russian]{babel}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{hyperref}

\title{Cryptographic Algorithms and Protocols for Distributed Ledgers}
\author{Kupriyanov K.I.\\Avdoshin S.M.}
\date{January 2019}

\begin{document}

\maketitle

\section*{RAW Abstract}
The Blockchain technology is typically associated with Bitcoin, because it was
the first system which has been distributed using the Blockchain technology.
As the technologies evolved, the number of various blockchains with different
kinds of applications had been drastically risen. A huge amount of blockchains
can be explained by various cryptographic algorithms and protocols usage in
them. It brought a problem of the absence of systematically gathered and
structured information about cryptographic algorithms and protocols in existing
distributed ledgers. The main objective of this work is to generalise all known
common cryptographic algorithms and protocols, which are being used nowadays.
The algorithms used in blockchains are going to be classified by common
metrics: time complexity, space complexity, and the resistance to hacking. It
is also intended to bring a programming library, where analyzed algorithms and
protocols are gathered in one place. The library would serve as a toolbox for
developers when creating a personal distributed ledger.  Structured information
and an accompanying programming toolbox will preliminary cause positive effect
on approaching extension in this area.

\section{Introduction}
Recent years have witnessed a growing academic interest to cryptocurrencies,
blockchains and distributed ledgers$^{\autoref{sec:ta}}$. The past ten years
have shown that the advance in the field of studying distributed ledgers and
cryptocurrencies is enormous compared to any other field in the past. One of
the results of the growing interest is thousands of researches carried out by
scientists and individuals. These researches initiated the creation of hundreds
cryptocurrencies and other uses of distributed ledgers. Some cryptocurrencies
repeat each other in the form of algorithms (hashing, crypto-) and protocols
used, but their spectrum is vast. Relatively little research has been carried
out on the algorithms used, and even less on protocols. The generalisability of
many published research on this issue is problematic. While most websites
provide non-scientific explanations, there is one study [1]TODOcitation, that
provides some aggregation of information on algorithms and protocols in
distributed ledgers. However, firstly, a number of technical and essential
questions remain about the classification of algorithms and protocols for
distributed ledgers, and secondly, it had only been carried in 2014, which
makes the information in it obsolete. New algorithms, modern applications of
old algorithms, new cryptocurrencies and their protocols are being released
every year, and nowadays there is a lot of possibilities to expand that area.
This prospective work is designed to investigate the usage of modern algorithms
and protocols in distributed ledgers and to make their up-to-date
classification. The aim is to extend the existent classification with new
algorithms and protocols, focusing on the broad scope of technologies and not
on their number.  According to plan, our detailed classification should reflect
actual condition in the field of distributed ledgers. One more important point
of the project is to collect all described implemented algorithms or code them
if they have not been done yet in a complete library for free usage. This
library will serve as a ``toolbox'' for a programmer who wants to build
cryptoledger combining known algorithms and protocols from the developed
library.
% -----------------------------------------
% 334 words
% -----------------------------------------

% Part of the aim of this project is to develop software that is compatible with
% The past thirty years have seen increasingly rapid advances in the field of ...

\section{Technical Aspects}\label{sec:ta}
A definition of a distributed ledger, as well as the difference between
distributed ledgers and blockchains must be given. A blockchain differs from a
traditional spreadsheet or from another ledger in case of being a
decentralized, distributed ledger, stored in a distributed databases of network
devices. People refer to it as ``distributed'' because no single entity manages
a distributed ledger system on its own. The ledger is distributed across a
network of computers, also known as ``nodes'', and each involved party has an
access to the ledger. This access allows all parties to receive real-time
status updates on transactions which occur within the network of nodes.

Each record of a transaction in a blockchain is represented by a timestamped
``block''. Whenever a new block is generated on a blockchain, the system
appends this block to the previous block using this blockchain’s unique
algorithm. The visual result of the process is one of a ``chain'' of blocks.
Hence the term ``blockchain''.

Not all distributed ledgers are blockchains. There are types of distributed
ledgers, which represent DAGs (Directed Acyclic Graphs), or some other
company-related data structure rather than the chain of blocks. But the
majority of distributed ledgers serve to the purpose of maintaining the
viability of cryptocurrencies. It does not mean that every Distributed Ledgers
Technology is used for creating cryptocurrencies. Some of them are being used
for different purposes, which are not covered in this paper.
% -----------------------------------------
% 242 words
% -----------------------------------------

\section{Problem Statement}
% Спорное (ноблинкрасивое) утверждение. А ДОКАЖИ ЧТО РИЛ БЫЛA recognized?!
The importance of creating a comprehensive classification of cryptographic
algorithms and protocols for distributed ledgers has recently been recognized
by the industry. However, the existing classification is expired, and there are
no any comprehensive study on them in the online sources. It may cause
difficult for a user, who wants to work with distributed ledgers (e.g.\
cryptocurrencies), problems to overcome. A {target user}\label{user} in terms
of this research is a user, who is concerned about security and cryptography
and who desires to reveal and understand algorithms are being used in the
technology which is going to be encountered. If an actor wants to know what
cryptographic algorithms and protocols is included when buying a
cryptocurrency, it might be difficult to find that out and to compare the
chosen one to other cryptocurrencies' algorithms and protocols. These are the
possible consequences of modern tendency for websites to be consumer-oriented
and provide only crisp and eye-appealing information. A major problem with this
approach is that selling a content pretends to be the primary goal whereas the
information delivery fades into the background. Consequently, it takes a long
time for average user to find out an underlying algorithms in a particular
distributed ledger.

Limitations of modern online ``blockchain creators'' is another problem for a
target user. Platforms, which are to deliver (e.g.\ ``cryptocurrency creation''
service), on average provide up to 3 algorithms and even less protocols. In
fact, in certain cases they do not provide user the ability to choose any
preferred protocol. Taking that into account a target user will not be able to
choose algorithms and protocol for his/her own ledger from the whole variety.
The limitations that those services put on the user are problematic.

In summary, there is a need for a better understanding of a
cryptoledger infrastructure and a structured approach in identifying and
collecting the majority of cryptographic algorithms and protocols that are
being used widely today. The following research questions
need to be considered:
\begin{itemize}
    \item What are the typical cryptographic algorithms found in various distributed ledgers;
    \item What are the typical cryptographic protocols found in various distributed ledgers;
    \item How to classify these algorithms for easier understanding and representing;
    \item What are the current industry practices as well as research advancements in each algorithm and protocol addressed;
    \item How to unify the knowledge gathered about cryptographic algorithms and protocols into one neat place;
    \item How to gather implemented algorithms and protocols into a programming
          library, which will be easy to use for creating own cryptoledger
          purpose?
\end{itemize}
% -----------------------------------------
% 415 words
% -----------------------------------------

\section{Objectives}
An initial objective of the project was to identify, analyze and classify the
broad scope of cryptographic algorithms and protocols in distributed ledgers.
The main aspect of the objective is the broad scope of algorithms and protocols
itself, not the quantity of distributed ledgers analyzed. It means that (e.g.\
some cryptocurrencies) may not be reviewd if algorithms and protocols they use
have already been classified. This goal also includes the implementation of the
programming library with algorithms and protocols for creating own
cryptoledger.
Particularly, the study has the following sub-objectives:
\begin{itemize}
    \item To provide a comprehensive review of cryptographic algorithms found
          in various distributed ledgers;
    \item To provide a comprehensive review of cryptographic protocols found in
          various distributed ledgers;
    \item To develop a robust classification method for easier understanding
          and representing;
    \item To review current industry practices and researches in regards to
          cryptographic algorithms and protocols in distributed ledgers;
    \item To outline a unification method for working with all gathered
          information on the topic;
    \item To outline a programming method, language and methodology for
          providing the library with algorithms and protocols reviewed.
\end{itemize}
The result of this study will be valuable to the industry practitioners (our
target users\(^{\ref{user}}\)) as well as researchers. The data gathered will
be concise, comprehensive, structured and easy to read. The program library is
supposed to be a complete toolbox for creating own cryptoledger, choosing from
a variety of gathered implemented algorithms and protocols.
% -----------------------------------------
% 220 words
% -----------------------------------------


\section{Preliminary Literature Preview}
Previous research [1] TODOcitation has established ``current ctyptoprotocol
infrastructure''. By 2014, it was a complete and comprehensive diagram, showing
all algorithms and protocols used in most popular distributed ledgers up to
that time. The analysis is also well-structured, but generalisable. What is
missing from the past study is a comprehensive and structured approach
in determining algorithms and protocols for cryptoledgers analyzed. However,
this study is the closest study to the topic discussed, and can be a great
point for taking-off with this research. The whitepapers for such technologies
as [bitcoin], [blockchain], [iota], [plasma], [ripple], [tkcoin] will surely be
used thruought conducting the research. The value of these monographies
consists of the following facts:
\begin{itemize}
    \item Whitepapers usually reveal algorithms and protocols used in a
          particular distributed ledger;
    \item Whitepapers usually point out the source code of algorithms and
          protocols, or even entire ledger.
\end{itemize}
% -----------------------------------------
% 144 words
% -----------------------------------------

\section{Methodology}
The primary research method for this study is the literature review and
benchmark analysis. Identification and classification of cryptographic
algorithms and protocols in distributed ledgers is the first and the main step
for reaching the aim of this work. This study will  review various types of
distributed ledgers, such as cryptocurrencies, and investigate their
characteristics firstly. Then, based on the understanding of the underlying
structure of every analyzed ledger, a list of all known algorithms and
protocols will be produced. In the third stage of this work, the new
classification will be developed. Finally, the programming part, where the
implementations of gathered cryptographic algorithms and protocols will be
assembled into a one complete library, will be done. This library will be a
toolbox for users who want to build a specified cryptoledger. The library
should be written in Python version 3.6.5 and published in a remote PyPI
repository. It should also be installable using ``pip'' utility with optional
``extra-url'' argument. This study will be conducted between November 2018 and
March 2019.
% -----------------------------------------
% 141 words
% -----------------------------------------

\section{Conclusion}
The anticipated results of this research may potentially show that
structured body of knowledge of cryptographic algorithms and protocols in
distributed ledgers as well as the library, containing all the algorithms
analyzed, may be useful for people who want to build own cryptoledger. People,
who is interested in how certain cryptoledgers are implemented, will also
benefet from this systematic research.

Looking ahead, published results will give public the ability to have an
in-depth view on rapid and dinamically-moving area in modern technology. As
well as the presented thesis, the pythonic library may potentially cause ripe
business development of small legal entities. Concluding the above, it could be
said, that the completed objective can make a huge effect on modern approaches
for distributed ledgers.

\section{References}

\end{document}

